\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2024 -- now}
      {Pullscription}{}
      \resumeItemListStart
        \resumeItem{Worked closely with Jago, the founder and CEO, to discuss, suggest, design, and implement the system structure for the organization's blog and shopping website, including both the customer and supplier end. The aim was to create an easy-to-maintain structure that is fast for users to access and optimized for SEO.}
        \resumeItem{Utilized Nginx and Docker to deploy the system on a server with CI/CD pipeline spported by GitHub Actions.}
        \resumeItem{Deployed and integrated the Matomo tracking system with a focus on privacy concerns and wrote unit tests.}
        \resumeItem{Collaborated closely with the team and provided guidance in implementing the website.}
        \resumeItem{Integrated Stripe for payment processing and Auth0 with JWT for authentication into the website, and wrote tests.}
        \resumeItem{Worked with the design team to create and implement a blog site using Nuxt with TypeScript and a shopping site for publishing and managing comic books, embedding abstract content of weekly news into the main website.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{January 2023 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with professors and researchers on projects. Published paper at FSE 2024. Submitted to CSCW 2026.}
        \resumeItem{Developed an universal user interaction tracking platform for VSCode, integrating Tobii Eye Tracker 5 to capture eye movement and user interactions across in-editor events, with a JavaScript frontend and C\# backend; reduced frontend-backend communication latency to one-tenth of the existing solution, tested over 80 hours with 33 users.}
        \resumeItem{Developed a high-accuracy algorithm in JavaScript and Python (using Hugging Face) to detect whether a video is a clip of another, outperforming existing solutions, and implemented a concurrent pool management tool to fully utilize a multicore cloud server.}
        \resumeItem{Worked on and deployed an online meeting platform left by a previous team, adding separate interfaces for facilitators and participants, Firebase for real-time communication, Daily.js for meetings, Assembly AI for transcription and data analysis, and GPT-based cues, resolving critical bugs and enabling 86 meetings.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2023 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Served as the sole or lead TA for several courses, including Java and Data Structures, Usability of Programming Languages, and Compilers. Received 'Excellent' ratings from instructors and a 90\%+ student recommendation rate.}
        \resumeItem{Developed several assignment and unit tests using JUnit on Docker, created templates with GitHub Actions, and helped students with the code merge process.}
        \resumeItem{Developed an interactive shell with session management using JSP and Servlets deployed on Azure, allowing students to try solutions online without exposing the source code. Successfully supported 30+ users simultaneously.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
