\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2024 -- now}
      {Pullscription}{}
      \resumeItemListStart
        \resumeItem{Worked closely with Jago, the founder and CEO, to discuss, suggest, design, and implement the system structure for the organization's blog and shopping website, including both the customer and supplier end. The aim was to create an easy-to-maintain structure that is fast for users to access and optimized for SEO.}
        \resumeItem{Utilized Nginx and Docker to deploy the system on a server with CI/CD pipeline spported by GitHub Actions.}
        \resumeItem{Deployed and integrated the Matomo tracking system with a focus on privacy concerns and wrote unit tests.}
        \resumeItem{Collaborated closely with the team and provided guidance in implementing the website.}
        \resumeItem{Integrated Stripe for payment processing and Auth0 with JWT for authentication into the website, and wrote tests.}
        \resumeItem{Worked with the design team to create and implement the blog site, embedding the abstract content into the main website and iOS app. Wrote unit tests for them.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{April 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Michael Coblenz on the usability analysis of Copilot.}
        \resumeItem{Designed an experiment using an eye tracker to evaluate the costs and benefits of Copilot for programmers who are new to React. And executing it now.}
        \resumeItem{Designed and implemented an universe eyetracking platform for native based VSCode to collect data, and analyzed data using JMP.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{April 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Kristen Vaccaro and Deepak Kumar, and collaborated with two other group members to assess political bias in YouTube's recommendation system.}
        \resumeItem{Developed a novel matching algorithm to pair long and short videos, outperforming all known approaches for our planned analysis. Designed a mixed-method approach to measure, collect, and evaluate outcome variables.}
        \resumeItem{Assessed methods for measuring the political leanings of media houses, utilizing AllSides and other existing models.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{April 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Jude Abishek Rayan under the guidance of Steven Dow on improving workshop communication protocols for projects CueHub and workshop management.}
        \resumeItem{For the CueHub project, I built, redesigned and tested a customized online meeting platform with automatic cue support and integrated monitoring tools based on the discussion results. Utilized GPTs to provide cues during meetings to improve communication. Wrote design decisions and implementation sections in the paper, and assisted in designing, engaging in discussions throughout the entire research workflow, and data analysis.}
        \resumeItem{For workshop management project, I designed and developed a 4-component workshop management system for real-time user engagement using prompt-engineered GPTs to foster better and more diversified idea generation via cues and discussed ways to improve communication for all groups during meetings.}
      \resumeItemListEnd

    \resumeSubheading
      {Researcher}{April 2024 -- now}
      {Independent}{}
      \resumeItemListStart
        \resumeItem{Worked with Jimmy Koppel on comparing and analyzing the advantages and disadvatanges of using tutorials over the Cody system.}
        \resumeItem{Discuss, design, and implement an analysis plan to examine the data and write a paper right now.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{January 2023 -- September 2023}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Michael Coblenz on the usability analysis of autocomplete.}
        \resumeItem{Designed and executed an experiment with 32 participants using an eye tracker to evaluate the costs and benefits of IDE-based autocomplete features for programmers using an unfamiliar API, analyzed data using JMP, performed thementic analysis, and published a paper on the Foundations of Software Engineering.}
        \resumeItem{Found that participants who used autocomplete learned more while spending less time reading documentation, although autocomplete did not significantly reduce the number of keystrokes required to complete tasks.}
        \resumeItem{Designed and implemented a consumer-level eye-tracking platform for web based VSCode, a Chrome extension, and a VSCode extension to collect data.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2023 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Major TA for Java and Data Structure courses (DSC30) with Soohyun Liao for two quarters.}
        \resumeItem{Sole TA for the Usability of Programming Languages course (CSE291) with Michael Coblenz for one quarter and TA for the same course for another quarter.}
        \resumeItem{Sole TA for Compilers (CSE 131) with Yufei Ding for one quarter, and Introduction to Data Visualization (DSC 106) with Sam Lau for another quarter.}
        \resumeItem{Guided group projects on programming languages and software engineering topics, and proposed, designed, and developed innovative course assignments.}
        \resumeItem{Managed course logistics, graded assignments, and collaborated with the professor and team members to refine course content. Conducted office hours and discussion sections to assist students and deepen their understanding.}
        \resumeItem{Received an 'Excellent' rating from the instructor, and over 90\% of the students gave a 'recommendation' rating in the course evaluations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
