\section{ Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teaching Assistant}{September 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{TA for the Usability of Programming Languages course (CSE291) with Michael Coblenz for one quarter.}
        \resumeItem{Lead class, discussions and office hours, graded assignments, and provided personalized advice to students.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2024 -- June 2024}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Sole TA for Compilers (CSE 131) with Yufei Ding for one quarter, and Introduction to Data Visualization (DSC 106) with Sam Lau for another quarter.}
        \resumeItem{Worked on designing course components, creating assignments, building grading scripts, making and grading exams, homework, and projects. Provided suggestions for course content and collected student feedback.}
        \resumeItem{Managed infrastructure and logistics, discussed course content, designed, refined, and graded homework, held office hours and discussion sections, and engaged students in discussions.}
        \resumeItem{Received an 'Excellent' rating from the instructor for both courses, and over 90\% of the students gave a 'recommend' rating in the course evaluations.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{September 2023 -- December 2023}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Sole TA for the Usability of Programming Languages course (CSE291) with Michael Coblenz for one quarter.}
        \resumeItem{Discussed course content with the professor, graded assignments, led discussions during lectures on specific course content, and provided personalized advice to students.}
        \resumeItem{Guided group projects on various topics related to the usability of programming languages or software engineering. Conducted office hours to assist students and gain insights through discussions.}
        \resumeItem{Received a 100\% 'recommend' rating from students in the course evaluations, while the professor rating was not applicable.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{January 2023 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Michael Coblenz on the usability analysis of autocomplete, designed, executed an experiment with 32 participants and published on the Foundations of Software Engineering.}
        \resumeItem{Worked with Michael Coblenz on the usability analysis of Copilot. Designed an experiment and executing it now.}
        \resumeItem{Designed and implemented a consumer-level universe eye-tracking platform for both web and native based VSCode, a Chrome extension and a VSCode extension to collect data.}
        \resumeItem{Worked with Kristen Vaccaro and Deepak Kumar, and collaborated with two other group members to assess bias in YouTube's recommendation system.}
        \resumeItem{Developed a method to match long and short items using a novel matching algorithm, and devised a mixed design to measure, collect, and evaluate outcome variables, such as the video leaning.}
        \resumeItem{Worked with Jude Abishek Rayan under the guidance of Steven Dow on improving conference communication protocols for projects CueHub and a conference management system.}
        \resumeItem{Designed, implemented, tested, and deployed software using React, Firebase, Flask, GitHub Actions, Cloudflare, and Oracle Cloud, based on the weekly discussion results. Improved the product in a rapid process and assisted in designing the entire research workflow.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2023 -- June 2023}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Major TA for Java and Data Structure courses (DSC30) with Soohyun Liao for two quarters.}
        \resumeItem{Proposed, designed, and developed new and innovative assignments and projects for the course, in collaboration with the professor. Graded students' assignments and collaborated with team members to discuss and refine course content.}
        \resumeItem{Held office hours and conducted all discussion sections to assist students in gaining a deeper understanding of course topics. Taught additional, non-required concepts during discussion sections.}
        \resumeItem{Received a 90\% 'recommend' rating from students in the course evaluations, while the professor rating was not applicable.}
      \resumeItemListEnd

    \resumeSubheading
      {Volunteer Tutor}{January 2021 -- May 2021}
      {University of Wisconsin-Madison}{}
      \resumeItemListStart
        \resumeItem{Helped students with their coursework related to computer science at the Computer Science Learning Center.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
