\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2024 -- now}
      {Pullscription}{}
      \resumeItemListStart
        \resumeItem{Worked closely with Jago, the founder and CEO, to discuss, suggest, design, and implement the system structure for the blog and website system for the organization, aiming to create an easy-to-maintain structure that is fast for user to access it and optimized for SEO.}
        \resumeItem{Utilized Nginx and Docker to deploy the system on a cloud server and implemented the CI/CD pipeline using GitHub Actions.}
        \resumeItem{Deployed and integrated the Matomo tracking system with a focus on privacy concerns.}
        \resumeItem{Collaborated closely with the team and provided guidance in implementing the website system.}
        \resumeItem{Implemented a payment system using Stripe and authentication using Auth0 on the existing website using Vue.}
        \resumeItem{Worked with the design team to create and implement the blog site, embedding the abstract content into the main website and iOS app.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{April 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Michael Coblenz on the usability analysis of Copilot.}
        \resumeItem{Designed an experiment using an eye tracker to evaluate the costs and benefits of Copilot for programmers who are new to React. And executing it now.}
        \resumeItem{Designed and implemented an universe eyetracking platform for native based VSCode to collect data, and analyzed data using JMP.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{April 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Kristen Vaccaro and Deepak Kumar, and collaborated with two other group members to assess political bias in YouTube's recommendation system.}
        \resumeItem{Developed a method to match long and short items using a newly developed matching algorithm, and devised a mixed design to measure, collect, and evaluate outcome variables.}
        \resumeItem{Evaluated methods to measure the current political leaning of media outlets based on AllSides and other existing models.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{April 2024 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Jude Abishek Rayan under the guidance of Steven Dow on improving conference communication protocols for projects CueHub and conference management.}
        \resumeItem{Built and tested software based on the discussion results, and assisted in designing the entire research workflow.}
      \resumeItemListEnd

    \resumeSubheading
      {Researcher}{April 2024 -- now}
      {Independent}{}
      \resumeItemListStart
        \resumeItem{Worked with Jimmy Koppel on comparing and analyzing the advantages of using tutorials over the Cody system.}
        \resumeItem{Evaluated interview results using thematic analysis to identify themes and compare them between groups.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Student Researcher}{January 2023 -- September 2023}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Worked with Michael Coblenz on the usability analysis of autocomplete.}
        \resumeItem{Designed and executed an experiment with 32 participants using an eye tracker to evaluate the costs and benefits of IDE-based autocomplete features for programmers using an unfamiliar API, analyzed data using JMP, performed thementic analysis, and published a paper on the Foundations of Software Engineering.}
        \resumeItem{Found that participants who used autocomplete learned more about the API while spending less time reading documentation, although autocomplete did not significantly reduce the number of keystrokes required to complete tasks.}
        \resumeItem{Designed and implemented a consumer-level eye-tracking platform for web based VSCode and a Chrome extension to collect data.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2023 -- now}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Major TA for Java and Data Structure courses (DSC30) with Soohyun Liao for two quarters.}
        \resumeItem{Sole TA for the Usability of Programming Languages course (CSE291) with Michael Coblenz for one quarter and TA for the same course for another quarter.}
        \resumeItem{Sole TA for Compilers (CSE 131) with Yufei Ding for one quarter, and Introduction to Data Visualization (DSC 106) with Sam Lau for another quarter.}
        \resumeItem{Guided group projects on programming languages and software engineering topics, and proposed, designed, and developed innovative course assignments.}
        \resumeItem{Conducted office hours and discussion sections to assist students and deepen their understanding.}
        \resumeItem{Managed course logistics, graded assignments, and collaborated with the professor and team members to refine course content.}
        \resumeItem{Received an 'Excellent' rating from the instructor, and over 90\% of the students gave a 'recommendation' rating in the course evaluations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
