\section{Other Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{June 2024 -- now}
      {Pullscription}{}
      \resumeItemListStart
        \resumeItem{Worked closely with Jago, the founder and CEO, to discuss, suggest, design, and implement the system structure for the organization's blog and shopping website, including both the customer and supplier end. The aim was to create an easy-to-maintain structure that is fast for users to access and optimized for SEO.}
        \resumeItem{Utilized Nginx and Docker to deploy the system on a server with CI/CD pipeline spported by GitHub Actions.}
        \resumeItem{Deployed and integrated the Matomo tracking system with a focus on privacy concerns and wrote unit tests.}
        \resumeItem{Collaborated closely with the team and provided guidance in implementing the website.}
        \resumeItem{Integrated Stripe for payment processing and Auth0 with JWT for authentication into the website, and wrote tests.}
        \resumeItem{Worked with the design team to create and implement the blog site, embedding the abstract content into the main website and iOS app. Wrote unit tests for them.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2024 -- June 2024}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Sole TA for Compilers (CSE 131) with Yufei Ding for one quarter, and Introduction to Data Visualization (DSC 106) with Sam Lau for another quarter.}
        \resumeItem{Worked on designing course components, creating assignments, building grading scripts, making and grading exams, homework, and projects. Provided suggestions for course content and collected student feedback.}
        \resumeItem{Managed infrastructure and logistics, discussed course content, designed, refined, and graded homework, held office hours and discussion sections, and engaged students in discussions.}
        \resumeItem{Received an 'Excellent' rating from the instructor for both courses, and over 90\% of the students gave a 'recommend' rating in the course evaluations.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{September 2023 -- December 2023}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Sole TA for the Usability of Programming Languages course (CSE291) with Michael Coblenz for one quarter.}
        \resumeItem{Discussed course content with the professor, graded assignments, led discussions during lectures on specific course content, and provided personalized advice to students.}
        \resumeItem{Guided group projects on various topics related to the usability of programming languages or software engineering. Conducted office hours to assist students and gain insights through discussions.}
        \resumeItem{Received a 100\% 'recommend' rating from students in the course evaluations, while the professor rating was not applicable.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{January 2023 -- June 2023}
      {University of California San Diego}{}
      \resumeItemListStart
        \resumeItem{Major TA for Java and Data Structure courses (DSC30) with Soohyun Liao for two quarters.}
        \resumeItem{Proposed, designed, and developed new and innovative assignments and projects for the course, in collaboration with the professor. Graded students' assignments and collaborated with team members to discuss and refine course content.}
        \resumeItem{Held office hours and conducted all discussion sections to assist students in gaining a deeper understanding of course topics. Taught additional, non-required concepts during discussion sections.}
        \resumeItem{Received a 90\% 'recommend' rating from students in the course evaluations, while the professor rating was not applicable.}
      \resumeItemListEnd

    \resumeSubheading
      {Volunteer Tutor}{January 2021 -- May 2021}
      {University of Wisconsin-Madison}{}
      \resumeItemListStart
        \resumeItem{Helped students with their coursework related to computer science at the Computer Science Learning Center.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Assistant}{January 2019 -- May 2019}
      {Illinois Institute of Technology}{}
      \resumeItemListStart
        \resumeItem{Tutored students in their computer science coursework at the university's academic resource center.}
        \resumeItem{Helped the organization advertise its services and events, and assisted in organizing and running events.}
      \resumeItemListEnd

    \resumeSubheading
      {Teaching Assistant}{August 2018 -- May 2019}
      {Illinois Institute of Technology}{}
      \resumeItemListStart
        \resumeItem{Instructed students in lab sessions of Java courses and held office hours to help students best understand class content.}
        \resumeItem{Regularly checked their homework, had discussions with the professor, and collaborated with team members on ways to improve the course and address major student challenges.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
