\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Pullscription websites} $|$ \emph{Vue, Vitepress, Auth0}}{2024}
    \resumeItemListStart
      \resumeItem{Designed a modern comic book shopping and blog site.}
\resumeItem{Integrated Stripe payment solution.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Pullscription blog websites} $|$ \emph{Vue, Vitepress, Auth0}}{2024}
    \resumeItemListStart
      \resumeItem{Designed a modern comic book shopping and blog site.}
\resumeItem{Integrated Stripe payment solution.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Video matching and Leaning rating system} $|$ \emph{Cloudflare Worker, HTML, JS}}{2024}
    \resumeItemListStart
      \resumeItem{An anonymous rating system for people to compare two matched videos and provide human feedback.}
\resumeItem{Designed puretext based algorithm to match two videos, outperform any existing video matching algorithm in internal tests.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Workshop Manager} $|$ \emph{Electron, React}}{2024}
    \resumeItemListStart
      \resumeItem{Designed and built a 4-component workshop manager for real-time user engagement.}
\resumeItem{Utilized Worker, GPTs, Socket, HTTPS, and DDNS.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Cross platform Markdown app} $|$ \emph{Electron, JavaScript}}{2024}
    \resumeItemListStart
      \resumeItem{Built two VSCode extension to help my own experiment.}
\resumeItem{}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Cue Hub} $|$ \emph{React, Firebase, Flask}}{2024}
    \resumeItemListStart
      \resumeItem{Worked on and deployed an online meeting platform with support for user communication and ideation.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{HealthCare Chatbot} $|$ \emph{Expo, Worker, GitHub, Jest, Vitest}}{2024}
    \resumeItemListStart
      \resumeItem{Led a group of five people to create a ChatBot with CI/CD pipelines.}
\resumeItem{Integrated design principles, Jest testing, and Agile methodologies.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Online interactive shell} $|$ \emph{JSP, Servlets, Java}}{2023}
    \resumeItemListStart
      \resumeItem{Built two VSCode extension to help my own experiment.}
\resumeItem{}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Java code style checker on gradescope} $|$ \emph{Shell, Java, Docker}}{2023}
    \resumeItemListStart
      \resumeItem{Built two VSCode extension to help my own experiment.}
\resumeItem{}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Eyetracker Monitoring Platform} $|$ \emph{C\#, JS, Tampermonkey, Chrome extension}}{2023, 2024}
    \resumeItemListStart
      \resumeItem{Developed a universe monitoring platform for tracking VSCode development process.}
\resumeItem{Integrated Tobii eye tracker 5.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{An economical computer} $|$ \emph{Node.js, GAMS, puppeteer}}{2022}
    \resumeItemListStart
      \resumeItem{Automatically scrape computer components' performance data weekly by simulating user behaviour and use optimization to find the best configuration.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Wise grader} $|$ \emph{JavaScript, TensorFlow, Tampermonkey}}{2021}
    \resumeItemListStart
      \resumeItem{Developed a program to aid quicker grading by suggesting scores based on length, N-gram analysis, and topic relevance for dictation questions.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Covid data report} $|$ \emph{Node.js, puppeteer}}{2021}
    \resumeItemListStart
      \resumeItem{Automatically scraped COVID data from various official sites by simulating user behaviour.}
\resumeItem{Pushed filtered results to subscribed users.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Energy Simulator} $|$ \emph{HTML, WebGL, JS, Java, JavaFX}}{2020}
    \resumeItemListStart
      \resumeItem{Enabled decision-making by solving linear problems and simulating energy usage.}
\resumeItem{Developed a website/Java GUI with 3D representation.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Financial Organization App} $|$ \emph{Expo, NLP.js}}{2020}
    \resumeItemListStart
      \resumeItem{Developed an app to organize expenses and income with voice interaction using locally hosted NLU for Capital One.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Financial Tutoring website} $|$ \emph{HTML, ejs, Worker}}{2020}
    \resumeItemListStart
      \resumeItem{Led a team to create a financial education website with tools like a yearly budgeting tool for Capital One.}
\resumeItem{Followed Agile methodologies.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{A JavaFx program} $|$ \emph{Java}}{2020}
    \resumeItemListStart
      \resumeItem{Developed a Java GUI program to manage and look up data among different farms.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{AutoCommenter} $|$ \emph{Java}}{2019}
    \resumeItemListStart
      \resumeItem{Automatically analyzed Java code and added comments based on preset rules.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{HateFate Website} $|$ \emph{HTML, JSP, SQL}}{2017}
    \resumeItemListStart
      \resumeItem{Led a four-person team to develop a website with core features.}
\resumeItem{Implemented login, signup with email verification, and user pairing.}
    \resumeItemListEnd
\resumeSubHeadingListEnd