\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Online interactive shell} $|$ \emph{Java Server Page, Servlets, Java, Azure}}{2023}
    \resumeItemListStart
      \resumeItem{Developed an interactive shell using JSP and Servlets deployed on Azure, enabling students to run Java source code online without accessing the source code, while supporting over 30 users simultaneously. The backend featured a custom connection session management utility to optimize resource usage and ensure seamless session handling.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Financial Tutoring website and app} $|$ \emph{HTML, Ejs, Worker, JavaScript, echarts, Expo, NLP}}{2020}
    \resumeItemListStart
      \resumeItem{Designed and led a team to develop a static financial education website for Capital One. The site includes interactive learning tools, such as quizzes and a self-built, stateless learning progress tracking system. It also has various utilities, including a personal expense management app.}
\resumeItem{Created detailed implementation guidance for group members and a user manual for the website and learning content. Build CI/CD pipelines and deployed them with GitHub Actions.}
\resumeItem{Built front end using embedded JavaScript for the main site and HTML with JavaScript for utility tools. Developed backend with JavaScript and deployed on Cloudflare Workers to handle requests, including the encryption and decryption of learning stage information using AES and crypto and a dynamically rendered quiz system. Users can download their encrypted learning progress and upload it to decode and resume learning, or use the same browser to continue learning. No data is stored on the server considering privacy and budget.}
\resumeItem{Developed a cross-platform personal finance app for Capital One that enables users to manage expenses and income via voice and chat interfaces using a local NLU engine, built with Expo for Android and iOS, tested and packaged for both platforms; Designed with JSON import/export for secure, local-only data storage and syncing.}
\resumeItem{Followed Agile methodologies, discussed with mentors and communicated with stakeholders to understand their needs and software development stages.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Energy Simulator} $|$ \emph{HTML, WebGL, JS, Java, JavaFX, Three.js, echarts}}{2020}
    \resumeItemListStart
      \resumeItem{Designed and developed a web-based energy simulation tool utilizing jsLPSolver to optimize energy sources based on historical data and project future trends via linear regression.}
\resumeItem{Presented results on a static website built with HTML and JavaScript, featuring a 3D energy system simulation using A-Frame and Three.js, with AR functionalities via QR codes, dynamic data visualization, and lightweight localization. Ensured full support for modern browsers and partial support for IE 11.}
\resumeItem{Reimplemented most functionalities in JavaFX without 3D representation.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{AutoCommenter} $|$ \emph{Java, JFrame}}{2019}
    \resumeItemListStart
      \resumeItem{Designed and developed a local utility program in Java with JFrame to analyze Java code on preset rules and semi-automatically add comments by integrating user input through typing or voice, with voice recognition powered by the iFlyTek API and translation supported by the Baidu Translation API.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{HateFate Website} $|$ \emph{HTML, Java Server Page, SQL, Java, Servlets}}{2017}
    \resumeItemListStart
      \resumeItem{Led a four-person team in developing a social networking website that connects users based on shared dislikes, with features including login, email-verified signup, and user pairing. Utilized Material design to create the interface.}
\resumeItem{Developed the frontend using HTML and JavaServer Pages (JSP) and built the backend with JSP and SQL for data storage. Deployed on the Azure cloud with an Azure SQL database.}
\resumeItem{Developed multiple login methods and utilized cookies to store user information, enabling automatic session recovery. Designed and integrated a custom mail system to handle email verification, password resets, and new match notifications using SMTP.}
\resumeItem{Secured the website with SSL encryption and employed a combination of MD5, public/private key encryption, and AES for data security during page forwarding and email verification.}
    \resumeItemListEnd
\resumeSubHeadingListEnd