\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{HealthCare Chatbot} $|$ \emph{Expo, Worker, GitHub, Jest, Vitest, Figma}}{2024}
    \resumeItemListStart
      \resumeItem{Led a team of five to create a chatbot with CI/CD pipelines using Agile methodologies. Self-delegate leadership roles when necessary. Consulted with experts in health care to understand their needs and requirements.}
\resumeItem{Developed a chatbot using Expo to provide healthcare information and answer questions via a fine-turned GPT service. Backend services were built with JavaScript and deployed on Cloudflare Workers to handle user information management, session storage,  authentication and token management, using salted hashes for password storage.}
\resumeItem{Learned methods for managing disputes and mediation conflicts within a team, including documenting divergence points and finding common ground. Realized the importance of communication in a team.}
\resumeItem{Integrated Material Design principles and conducted unit tests using Jest for the Expo app and Vitest for the middleware server. Utilized GitHub Actions for the CI/CD pipeline.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{Financial Tutoring website and app} $|$ \emph{HTML, Ejs, Worker, JavaScript, echarts, Expo, NLP}}{2020}
    \resumeItemListStart
      \resumeItem{Designed and led a team to develop a static financial education website for Capital One. The site includes interactive learning tools, such as quizzes and a self-built, stateless learning progress tracking system. It also has various utilities, including a personal expense management app.}
\resumeItem{Created detailed implementation guidance for group members and a user manual for the website and learning content. Build CI/CD pipelines and deployed them with GitHub Actions.}
\resumeItem{Built front end using embedded JavaScript for the main site and HTML with JavaScript for utility tools. Developed backend with JavaScript and deployed on Cloudflare Workers to handle requests, including the encryption and decryption of learning stage information using AES and crypto and a dynamically rendered quiz system. Users can download their encrypted learning progress and upload it to decode and resume learning, or use the same browser to continue learning. No data is stored on the server considering privacy and budget.}
\resumeItem{Developed a cross-platform personal finance app for Capital One that enables users to manage expenses and income via voice and chat interfaces using a local NLU engine, built with Expo for Android and iOS, tested and packaged for both platforms; Designed with JSON import/export for secure, local-only data storage and syncing.}
\resumeItem{Followed Agile methodologies, discussed with mentors and communicated with stakeholders to understand their needs and software development stages.}
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{HateFate Website} $|$ \emph{HTML, Java Server Page, SQL, Java, Servlets}}{2017}
    \resumeItemListStart
      \resumeItem{Led a four-person team in developing a social networking website that connects users based on shared dislikes, with features including login, email-verified signup, and user pairing. Utilized Material design to create the interface.}
\resumeItem{Developed the frontend using HTML and JavaServer Pages (JSP) and built the backend with JSP and SQL for data storage. Deployed on the Azure cloud with an Azure SQL database.}
\resumeItem{Developed multiple login methods and utilized cookies to store user information, enabling automatic session recovery. Designed and integrated a custom mail system to handle email verification, password resets, and new match notifications using SMTP.}
\resumeItem{Secured the website with SSL encryption and employed a combination of MD5, public/private key encryption, and AES for data security during page forwarding and email verification.}
    \resumeItemListEnd
\resumeSubHeadingListEnd