
\section{Publications}

 \resumeItemListStart
      \resumeItem{Shaokang Jiang and Michael Coblenz. \textbf{An Analysis of the Costs and Benefits of Autocomplete in IDEs}. In proceedings of the ACM on Software Engineering (FSE 2024) (25\% acceptance rate)}
      \resumeItem{Shaokang Jiang, Jimmy Koppel, Michael Coblenz. \textbf{Questions Before Answers? A Comparison of Codebase Chatbots and Tutorials for Codebase Learning}. In Plateau Workshop (Plateau 2025) }
      \resumeItem{Jude Rayan, Shaokang Jiang, Nishant Balaji, Jinmao Wang, Ian Gross, Cole Biehle, Steven P. Dow. \textbf{Cueing the Crowd: LLM-Driven Conversational Cues Across Different Meeting Modalities Increase Topical Diversity of Generated Ideas}. In proceedings of the ACM Collective Intelligence Conference (CI 2025) }
      \resumeItem{Shaokang Jiang and Michael Coblenz. \textbf{How LLMs Affect Developers' Productivity and Learning}. Under review.  Proceedings of the International Conference on Software Engineering (ICSE 2026) }
      \resumeItem{Shaokang Jiang, Arshia Arya, Seoyoung Kweon, Ivan Liang, Deepak Kumar, Kristen Vaccaro. \textbf{Long Story Short: Auditing Political Polarization in Recommendations for Long- vs. Short-form Videos on YouTube}. Under review. Proceedings of the ACM on Web Conference (WWW 2026)}
      % \resumeItem{Shaokang Jiang and Michael Coblenz. \textbf{An Analysis of the Costs and Benefits of Copilot in IDEs}. WIP. Planned for proceedings of the International Conference on Software Engineering (ICSE 2026) }
      % \resumeItem{Arshia Arya, Seoyoung Kweon, Shaokang Jiang, Ivan Liang, Kristen Vaccaro, Deepak Kumar. \textbf{Assessing political polarization on YouTube Shorts}. WIP. Planned for proceedings of the ACM on Human-Computer Interaction (PACM HCI) (CSCW 2026) }
    \resumeItemListEnd