
\section{Experience}

\outerlist{

	\entryexp
	{\textbf{Teaching Assistant} | University of California San Diego}{Jan 2024\textendash now}
	\innerlist{
		\entry{Ta worked with Sam Lau for Introduction for Data Visualization (DSC 106) for one quarter. And Sole Ta worked with Yufei Ding for Compilers (CSE 131) for one quarter}
		\entry{Working on infrastructure and logistics management. Had discussions with the professor about the course content, designing, polishing, and grading homework, holding office hours and discussion sections, and engaging students in discussions.}
	}



	\entryexp
	{\textbf{Teaching Assistant} | University of California San Diego}{Sept 2023\textendash Dec 2023}
	\innerlist{
		\entry{Sole Ta worked with Michael Coblenz for the usability of the programming language course (CSE291) for one quarter. }
		\entry{Had discussions with the professor about the content of this course, graded assignments, hosted some discussions during the main lecture covering specific course content, and provided personalized advice to individual students.}
		\entry{Offered guidance on group projects covering a variety of topics in the usability of programming language or software engineering. Conducted office hours to assist students and mined for insights while discussing with them.}
	}

	\entryexp
	{\textbf{Graduate student researcher} | University of California San Diego}{Jan 2023\textendash Sept 2023}
	\innerlist{
		\entry{Worked with Michael Coblenz on the usability analysis of autocomplete.}
		\entry{Designed and executed an experiment with 32 participants using an eye tracker to evaluate the costs and benefits of IDE-based autocomplete features to programmers who use an unfamiliar API; analyzed data using JMP; and wrote a paper for the study.}
		\entry{Found that participants who used autocomplete learned more about the API while spending less time reading the documentation; found autocomplete did not significantly reduce the number of keystrokes required to finish tasks.}
		\entry{Acquired fundamental skills in conducting empirical research studies and learned various methods for handling and understanding the implications of eye-tracking data.}
	}

	\entryexp
	{\textbf{Teaching Assistant} | University of California San Diego}{Jan 2023\textendash Jun 2023}
	\innerlist{
		\entry{Major Ta worked with Soohyun Liao for Java and data structure courses (DSC30) for two quarters.}
		\entry{Proposed, designed, and developed entirely new and innovative assignments and projects for the entire course, most of which had never been used elsewhere, in collaboration with the professor.  Graded students' assignments. Collaborated with team members to discuss and refine the content of the course.}
		\entry{Held office hours and conducted all discussion sections to assist students in gaining a deeper understanding of the course topics. Taught some additional but not required concepts during discussion sections.}
	}

	\entryexp
	{\textbf{Volunteer Tutor} | University of Wisconsin-Madison}{Jan 2021\textendash May 2021}
	\innerlist{
		\entry{Help students with their coursework related to computer science at computer science learning center.}
	}

	\entryexp
	{\textbf{Teaching Assistant} | Illinois Institute of Technology}{Aug 2018\textendash May 2019}
	\innerlist{
		\entry{Instructed students in lab sessions of Java courses and held office hours to help students best understand class content}
		\entry{Checked their homework regularly and had discussions with the professor and collaborated with team members about ways to improve this course and solve the major problems of students.}
	}

	\entryexp
	{\textbf{Student Assistant} | Illinois Institute of Technology}{Jan 2019\textendash May 2019}
	\innerlist{
		\entry{Tutoring students with their coursework related to computer science in the university's academic resource center}
	}

	\entryexp
	{\textbf{Research Assistant} | Illinois Institute of Technology}{Jan 2019\textendash May 2019}
	\innerlist{
		\entry{Modified POW (Bitcoin) and POS (EOSIO) blockchain source code for execution on a blockchain emulator, facilitating performance measurement for researchers.}
	}


}
