
\section{Experience}

\outerlist{

\entryexp
	{\textbf{Graduate student researcher} | University of California San Diego}{April 2024\textendash now}
\innerlist{
	\entry{Work with Michael Coblenz on the usability analysis of copilot.}
	\entry{Designed and executing an experiment now using an eye tracker to evaluate the costs and benefits of copilot to programmers who are new to React.}
}

\entryexp
	{\textbf{Graduate student researcher} | University of California San Diego}{April 2024\textendash now}
\innerlist{
	\entry{Work with Kristen Vaccaro and Deepak Kumar, collaborate with other two group memebers on the assessing political bias about youtube recommendation system.}
	\entry{Worked on a method to match long and short items using a newly developed matching algorithm by me, and devised a mixed design to measure, collect, and evaluate outcome variables.}
	\entry{Worked on evaluation methods to measure the current political leaning of all media houses based on AllSides and various existing models.}
}

\entryexp
	{\textbf{Graduate student researcher} | University of California San Diego}{April 2024\textendash now}
\innerlist{
	\entry{Worked with Jude Abishek Rayan under the guidance of Steven Dow on improving conference communication protocal for two projects, CueHub and conference management.}
	\entry{Built and tested the software based on the discussion results. Assisted with designing the entire research workflow.}
}

\entryexp
	{\textbf{Researcher} | Independent}{April 2024\textendash now}
\innerlist{
	\entry{Worked with Jimmy on comparing and analyzing the advantagement of using tutorial than the cody system.}
	\entry{Evaluated the interview results using thematic analysis to identify themes and compare them between groups.}
}

	\entryexp
	{\textbf{Teaching Assistant} | University of California San Diego}{Jan 2024\textendash Jun 2024}
	\innerlist{
		\entry{Sole Ta worked with Yufei Ding for Compilers (CSE 131) for one quarter. And ta worked with Sam Lau for Introduction for Data Visualization (DSC 106) for one quarter}
		\entry{Worked on designing course components, creating assignments, building scripts for grading, making and grading exams, homework, and projects. Provided suggestions to course content and collected student feedback. }
		\entry{Worked on infrastructure and logistics management, had discussions about the course content, designed, polished, and graded homework, held office hours and discussion sections, and engaged students in discussions.}
	}

	\entryexp
	{\textbf{Teaching Assistant} | University of California San Diego}{Sept 2023\textendash Dec 2023}
	\innerlist{
		\entry{Sole Ta worked with Michael Coblenz for the usability of the programming language course (CSE291) for one quarter. }
		\entry{Had discussions with the professor about the content of this course, graded assignments, hosted some discussions during the main lecture covering specific course content, and provided personalized advice to individual students.}
		\entry{Offered guidance on group projects covering a variety of topics in the usability of programming language or software engineering. Conducted office hours to assist students and mined for insights while discussing with them.}
	}

	\entryexp
	{\textbf{Graduate student researcher} | University of California San Diego}{Jan 2023\textendash Sept 2023}
	\innerlist{
		\entry{Worked with Michael Coblenz on the usability analysis of autocomplete.}
		\entry{Designed and executed an experiment with 32 participants using an eye tracker to evaluate the costs and benefits of IDE-based autocomplete features to programmers who use an unfamiliar API, analyzed data using JMP, and wrote a paper for the study.}
		\entry{Found that participants who used autocomplete learned more about the API while spending less time reading the documentation, found autocomplete did not significantly reduce the number of keystrokes required to finish tasks.}
		\entry{Acquired fundamental skills in conducting empirical research studies and learned various methods for handling and understanding the implications of eye-tracking data.}
	}

	\entryexp
	{\textbf{Usability of PL course project} | University of California San Diego}{Sept 2022\textendash Dec 2022}
	\innerlist{
	\entry{Worked on investigating whether Python Type Hints are helpful for competitive programmers (CP).}
	\entry{Designed and executed the experiment with 4 participants.}
	\entry{Did not find Python type hints to be significantly more useful for competitive programming in terms of task completion time and debugging time.}
	\entry{Thematic analyzed Survey results indicate that programmers also dislike type hints and autocomplete suggestions because they are annoying.}
	}
	
	\entryexp
		{\textbf{HCI research course project} | University of California San Diego}{Sept 2023\textendash Dec 2023}
	\innerlist{
		\entry{Investigating whether an avatar appearing in the ChatGPT interface would help create a better communication environment between humans and machines, particularly in terms of alleviating loneliness.}
	}
	
	\entryexp
	{\textbf{Teaching Assistant} | University of California San Diego}{Jan 2023\textendash Jun 2023}
	\innerlist{
		\entry{Major Ta worked with Soohyun Liao for Java and data structure courses (DSC30) for two quarters.}
		\entry{Proposed, designed, and developed entirely new and innovative assignments and projects for the entire course, most of which had never been used elsewhere, in collaboration with the professor.  Graded students' assignments. Collaborated with team members to discuss and refine the content of the course.}
		\entry{Held office hours and conducted all discussion sections to assist students in gaining a deeper understanding of the course topics. Taught some additional but not required concepts during discussion sections.}
	}

	\entryexp
	{\textbf{Volunteer Tutor} | University of Wisconsin-Madison}{Jan 2021\textendash May 2021}
	\innerlist{
		\entry{Help students with their coursework related to computer science at computer science learning center.}
	}

	\entryexp
	{\textbf{Teaching Assistant} | Illinois Institute of Technology}{Aug 2018\textendash May 2019}
	\innerlist{
		\entry{Instructed students in lab sessions of Java courses and held office hours to help students best understand class content}
		\entry{Checked their homework regularly and had discussions with the professor and collaborated with team members about ways to improve this course and solve the major problems of students.}
	}

	\entryexp
	{\textbf{Student Assistant} | Illinois Institute of Technology}{Jan 2019\textendash May 2019}
	\innerlist{
		\entry{Tutoring students with their coursework related to computer science in the university's academic resource center}
	}

	\entryexp
	{\textbf{Research Assistant} | Illinois Institute of Technology}{Jan 2019\textendash May 2019}
	\innerlist{
		\entry{Modified POW (Bitcoin) and POS (EOSIO) blockchain source code for execution on a blockchain emulator, facilitating performance measurement for researchers.}
	}
}
